Figures

### 2019-08-05 figures/07_model-selection.Rmd
viz global re coefs

>>>>

```{r re-comparison}
# tp, tn
# ag, row_crop, pasture, corn, soybeans
re_global <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
re_global$term <- unlist(lapply(re_brms, 
                                function(x) get_re_text(as.character(x$formula)[1])))
re_global$response <- c(rep("tp", 5), rep("tn", 5))
re_global <- dplyr::filter(re_global, term != "rowvcropvpct")

# loo_compare(loo(re_brms[[1]]), loo(re_brms[[2]]), loo(re_brms[[3]]),
#             loo(re_brms[[4]]), loo(re_brms[[5]]))
# loo_compare(loo(re_brms[[6]]), loo(re_brms[[7]]), loo(re_brms[[8]]), 
#             loo(re_brms[[9]]), loo(re_brms[[10]]))

group_by(re_global, response) %>%
  arrange(desc(`50%`))

gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`), color = "red") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = -0.2) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line(), 
        axis.text.y = element_blank()) +
  ggtitle("TN")

gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`), color = "red") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = -0.2) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line()) +
  ggtitle("TP")

cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.8))
```
